Wealth dynamics in the presence of network structure and primitive cooperation

### 2019-07-12 manuscript/analysis.tex
(Add reminders.)
Add Gini history plot (figure 3).

Figure~\ref{fig:effectiveWealthSingleRun} shows the same information in another
way: instead of plotting each agent's \textit{personal} wealth (as in the top
plot of Figure~\ref{fig:singleRun}, we show its \textbf{effective wealth},
defined as the sum of its personal wealth and its ``share'' of its proto's
wealth (if any). After all, contributions that a proto's members make to its
balance are available to those members in times of need; therefore, a fair
comparison between isolates and non-isolates should take this into account.
From the figure, it can be seen that isolates no longer have a systematic
advantage (as they appeared to in Figure~\ref{fig:singleRun}.

@@

>>>>

Figure~\ref{fig:effectiveWealthSingleRun} shows the same information in another
way: instead of plotting each agent's \textit{personal} wealth (as in the top
plot of Figure~\ref{fig:singleRun}), we show its \textbf{effective wealth},
defined as the sum of its personal wealth and its ``share'' of its proto's
wealth (if any). After all, contributions that a proto's members make to its
balance are available to those members in times of need; therefore, a fair
comparison between isolates and non-isolates should take this into account.
From the figure, it can be seen that isolates no longer have a systematic
advantage (as they appeared to in Figure~\ref{fig:singleRun}.)

@@

To see how wealth inequality plays out over time, we plot the Gini coefficient
of the population in Figure~\ref{fig:giniHistory}. (The Gini calculation is
taken with respect to each agent's \textit{effective} wealth, not merely its
personal wealth.) In stage 2, we see inequality decrease as agents join one
another in protos and contribute their ``excess'' wealth to a shared pool. When
the stage 3 starvation period commences, inequality rises as the poorer agents
drop to zero and begin to deplete proto balances.

\begin{figure}[hb]
\centering
\includegraphics[width=\columnwidth]{figures/giniHistory.png}
\caption{The simulated society's wealth inequality over time. (The same
simulation parameters were used as in Figures~\ref{fig:singleRun} and
\ref{fig:effectiveWealthSingleRun}, but this time with 500 agents.)}
\label{fig:giniHistory}
\end{figure}

% Note that the empty graph can't really be shown because stages 2 and 3 have
% no well-defined meaning in that case.

% Show Gini plot, null hypothesis, "this is why it doesn't matter"
